Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-04-18 manuscript/supplemental_material.Rnw
clearpage after each species, not before

<<top.expressed.genes,echo=FALSE,results="asis">>=
for (this.species in names(species.names)) {
    this.caption <- paste0("\\textit{",
                           capfirst(this.species),"} Placental Gene Expression of all genes with FPKM $\\ge 50$")
    cat(paste0("\\subsubsection{\\textit{",capfirst(this.species),"} Placental Gene Expression}\n\n"))
    xt.align <- c("r","l","l","p{2.5in}","r")
    if (this.species == "homo sapiens" || this.species == "ateles fusciceps") {
        xt.align <- xt.align[-2]
    }
    print(xtable(genes.expression.table(species.name=this.species),
                 caption=this.caption,
                 align=xt.align,
                 label=paste0("tab:all_",gsub(" ","_",this.species),"_placenta")
                 ),
          booktabs=TRUE,
          tabular.environment="longtable",
          floating=FALSE,
          caption.placement="top",
          sanitize.text.function=genes.table.sanitize,
          size="\\tiny"
          )
}
@

>>>>

<<top.expressed.genes,echo=FALSE,results="asis">>=
for (this.species in names(species.names)) {
    this.caption <- paste0("\\textit{",
                           capfirst(this.species),"} Placental Gene Expression of all genes with FPKM $\\ge 50$")
    cat(paste0("\\subsubsection{\\textit{",capfirst(this.species),"} Placental Gene Expression}\n\n"))
    xt.align <- c("r","l","l","p{2.5in}","r")
    if (this.species == "homo sapiens" || this.species == "ateles fusciceps") {
        xt.align <- xt.align[-2]
    }
    print(xtable(genes.expression.table(species.name=this.species),
                 caption=this.caption,
                 align=xt.align,
                 label=paste0("tab:all_",gsub(" ","_",this.species),"_placenta")
                 ),
          booktabs=TRUE,
          tabular.environment="longtable",
          floating=FALSE,
          caption.placement="top",
          sanitize.text.function=genes.table.sanitize,
          size="\\tiny"
          )
    cat("\\clearpage\n")
}
@
